Tulai

### 2023-11-18 paper/paper.qmd
edited map
Modify the plot with uppercase x axis and lowercase y axis for chi-square test

# using http://bboxfinder.com/ to get this
bbox = c(
  42, # left
  30, # lower
  51, # right
  38) # upper

@@

ggcorrplot(chisq$residuals,
           method = 'circle') + 
  ggplot2::scale_fill_gradient2(
    low = 'red',
    high = 'royalblue',
    mid = 'white',
    midpoint = 0,
    limit = c(-7, 11),
    space = "Lab",
    name = "Residual"
  ) + 
  coord_flip()

@@

ggcorrplot(chisq$residuals,
           method = 'circle') + 
  ggplot2::scale_fill_gradient2(
    low = 'red',
    high = 'royalblue',
    mid = 'white',
    midpoint = 0,
    limit = c(-7, 11),
    space = "Lab",
    name = "Residual"
  ) + 
  coord_flip()

>>>>

# using http://bboxfinder.com/ to get this
bbox = c(
  42, # left
  31, # lower
  50, # right
  37) # upper

@@

ggcorrplot(chisq$residuals,
           method = 'circle') + 
  scale_y_discrete(labels = function(y) str_to_upper(y)) +  
  scale_x_discrete(labels = function(x) str_to_lower(x)) +   
  ggplot2::scale_fill_gradient2(
    low = 'red',
    high = 'royalblue',
    mid = 'white',
    midpoint = 0,
    limit = c(-7, 11),
    space = "Lab",
    name = "Residual"
  ) + 
  coord_flip()

@@

ggcorrplot(chisq$residuals,
           method = 'circle') + 
  scale_y_discrete(labels = function(y) str_to_upper(y)) +  # Convert x axis labels to uppercase
  scale_x_discrete(labels = function(x) str_to_lower(x)) +  # Convert x axis labels to uppercase
  ggplot2::scale_fill_gradient2(
    low = 'red',
    high = 'royalblue',
    mid = 'white',
    midpoint = 0,
    limit = c(-7, 11),
    space = "Lab",
    name = "Residual"
  ) + 
  coord_flip()
